\bf Towards Pandemic-Scale Ancestral Recombination Graphs of SARS-CoV-2

### 2023-06-03 paper.tex
Updates from Overleaf

\title{Towards Pandemic-Scale Ancestral Recombination Graphs of SARS-CoV-2}
\author[1]{Shing H. Zhan}
\author[2,3$\star$]{Anastasia Ignatieva}
\author[1$\star$]{Yan Wong}
\author[4]{Katherine Eaton}
\author[1]{Benjamin Jeffery}
\author[1]{Duncan S. Palmer}
\author[4]{Carmen L. Murall}
\author[5]{Sarah P. Otto}
\author[1$\dagger$]{Jerome Kelleher}
\affil[1]{Big Data Institute, Li Ka Shing Centre for Health
Information and Discovery, University of Oxford, Oxford, United Kingdom}
\affil[2]{Department of Statistics, University of Oxford, Oxford, United Kingdom}
\affil[3]{School of Mathematics and Statistics, University of Glasgow, Glasgow, United Kingdom}
\affil[4]{National Microbiology Laboratory, Public Health Agency of Canada, Canada}
\affil[5]{Department of Zoology and Biodiversity Research Centre,
University of British Columbia, Vancouver, British Columbia, Canada}
\affil[$\star$]{Joint second author}
\affil[$\dagger$]{Correspondence: jerome.kelleher@bdi.ox.ac.uk}

>>>>

\title{\bf Towards Pandemic-Scale Ancestral Recombination Graphs of SARS-CoV-2}
\author[1]{Shing H. Zhan}
\author[2,3$\star$]{Anastasia Ignatieva}
\author[1$\star$]{Yan Wong}
\author[4]{Katherine Eaton}
\author[1]{Benjamin Jeffery}
\author[1]{Duncan S. Palmer}
\author[4]{Carmen L. Murall}
\author[5]{Sarah P. Otto}
\author[1$\dagger$]{Jerome Kelleher}
\affil[1]{\normalsize Big Data Institute, Li Ka Shing Centre for Health
Information and Discovery, University of Oxford, Oxford, United Kingdom}
\affil[2]{Department of Statistics, University of Oxford, Oxford, United Kingdom}
\affil[3]{School of Mathematics and Statistics, University of Glasgow, Glasgow, United Kingdom}
\affil[4]{National Microbiology Laboratory, Public Health Agency of Canada, Canada}
\affil[5]{Department of Zoology and Biodiversity Research Centre,
University of British Columbia, Vancouver, British Columbia, Canada}
\affil[$\star$]{Joint second author}
\affil[$\dagger$]{Correspondence: jerome.kelleher@bdi.ox.ac.uk}

% \author{
% Shing H.~Zhan \thanks{Big Data Institute, Li Ka Shing Centre for Health
% Information and Discovery, University of Oxford, Oxford, United Kingdom} \and Anastasia Ignatieva
% \thanks{Department of Statistics, University of Oxford, Oxford, United Kingdom}
% }
